Bird beak's elaboration and innovation

### 2022-08-04 Analysis/01-Data_preparation.Rmd
Cleaned up figure names

## Make a dispRity object and get axes data
shape_axes <- select.axes(custom.subsets(shapespace, group = clades))
form_axes  <- select.axes(custom.subsets(formspace, group = clades))
```

>>>>

## Make a dispRity object and get axes data
shape_axes <- select.axes(custom.subsets(shapespace, group = clades))
form_axes  <- select.axes(custom.subsets(formspace, group = clades))

pdf(file = "../Manuscript/Figures/axis_selection.pdf", height = 8, width = 12)
plot(shape_axes)
dev.off()
```

### 2022-08-04 Analysis/03.1-Elaboration_innovation_analysis[statistics].Rmd
Cleaned up figure names

## tex results
make.xtable(all_results[, -c(4, 6:8)], digit = 3, caption = "Posterior variance-covariance ellipses results for each clade compared to their parent clade or their parent parents clade (Comparison). n = the number of species per group. sd = the standard deviation of the ellipses orientation (across the posterior distribution). orthogonality = the degree of right angle for each group compared to their parent or parent's group (0 = parellel, 1 = orthogonal). Post. prob = the posterior probability of the orthogonality in the focal group being different from the comparison one (the 95% CI is from the randomised posterior probabilities).", label = "tab_ortho_results", longtable = FALSE, path = "../Manuscript/Tables/", include.rownames = FALSE)
```

@@

pdf("../Manuscript/Figures/Relative_EI.pdf", height = 8, width = 8)
par(mfrow = c(2,2))
plot.density(species = c(elaboration_species),
             group   = c(unlist(elaboration_super_orders), unlist(elaboration_orders)),
             xlab    = "relative elaboration", scale.x = TRUE,
             ylab    = "density",
             main    = "A - Total posterior elaboration per group\n(scaled) and per species")
legend("topright", lty = 1, legend = c("species", "groups"), col = c("blue", "orange"))
plot.density(species = c(innovation_species),
             group   = c(unlist(innovation_super_orders), unlist(innovation_orders)),
             xlab    = "relative innovation", scale.x = TRUE,
             ylab    = "density",
             main    = "B - Total posterior innovation per group\n(scaled) and per species")
plot.density(elaboration_species_auc, elaboration_group_auc, scale.x = FALSE, col = c("blue", "orange"), ylab = "density",
             xlab = "Posterior area under the curve (elaboration)",
             main = paste0("C - Difference in amounts of elaboration\nper group or per species\nBhattacharyya coefficient = ",
                           round(bhatt.coeff(elaboration_species_auc, elaboration_group_auc), 3)))
plot.density(innovation_species_auc, innovation_group_auc, scale.x = FALSE, col = c("blue", "orange"), ylab = "density",
             xlab = "Posterior area under the curve (innovation)",
             main = paste0("D - Difference in amounts of innovation\nper group or per species\nBhattacharyya coefficient = ",
                           bhatt.coeff(innovation_species_auc, innovation_group_auc)))
dev.off()
```

>>>>

## tex results
to_export <- all_results[, -c(4, 6:8)]
colnames(to_export)[c(6,9)] <- "2.5\\%"
colnames(to_export)[c(7,10)] <- "97.5\\%"
make.xtable(to_export, digit = 3, caption = "Posterior variance-covariance ellipses results for each clade compared to their parent clade or their parent parents clade (Comparison). n = the number of species per group. sd = the standard deviation of the ellipses orientation (across the posterior distribution). orthogonality = the degree of right angle for each group compared to their parent or parent's group (0 = parellel, 1 = orthogonal). Post. prob = the posterior probability of the orthogonality in the focal group being different from the comparison one (the 95\\% CI is from the randomised posterior probabilities).", label = "tab_ortho_results", longtable = FALSE, path = "../Manuscript/Tables/", include.rownames = FALSE)
```

@@

pdf("../Manuscript/Figures/relative_EI.pdf", height = 8, width = 8)
par(mfrow = c(2,2))
plot.density(species = c(elaboration_species),
             group   = c(unlist(elaboration_super_orders), unlist(elaboration_orders)),
             xlab    = "relative elaboration", scale.x = TRUE,
             ylab    = "density",
             main    = "A - Total posterior elaboration per group\n(scaled) and per species")
legend("topright", lty = 1, legend = c("species", "groups"), col = c("blue", "orange"))
plot.density(species = c(innovation_species),
             group   = c(unlist(innovation_super_orders), unlist(innovation_orders)),
             xlab    = "relative innovation", scale.x = TRUE,
             ylab    = "density",
             main    = "B - Total posterior innovation per group\n(scaled) and per species")
plot.density(elaboration_species_auc, elaboration_group_auc, scale.x = FALSE, col = c("blue", "orange"), ylab = "density",
             xlab = "Posterior area under the curve (elaboration)",
             main = paste0("C - Difference in amounts of elaboration\nper group or per species\nBhattacharyya coefficient = ",
                           round(bhatt.coeff(elaboration_species_auc, elaboration_group_auc), 3)))
plot.density(innovation_species_auc, innovation_group_auc, scale.x = FALSE, col = c("blue", "orange"), ylab = "density",
             xlab = "Posterior area under the curve (innovation)",
             main = paste0("D - Difference in amounts of innovation\nper group or per species\nBhattacharyya coefficient = ",
                           bhatt.coeff(innovation_species_auc, innovation_group_auc)))
dev.off()
```

### 2022-08-04 Analysis/06-Figure2_with_correlations.Rmd
Cleaned up figure names

```{r, echo = TRUE, eval = TRUE}
## Set the pdf parameters
pdf("../Manuscript/Figures/Figure2_correlations.pdf", height = 12, width = 8)

@@

```{r, echo = TRUE, eval = TRUE}
## Set the pdf parameters
pdf("../Manuscript/Figures/Figure2_correlations_passeriformes.pdf", height = 12, width = 6)

>>>>

```{r, echo = TRUE, eval = TRUE}
## Set the pdf parameters
pdf("../Manuscript/Figures/correlations.pdf", height = 12, width = 8)

@@

```{r, echo = TRUE, eval = TRUE}
## Set the pdf parameters
pdf("../Manuscript/Figures/correlations_passeriformes.pdf", height = 12, width = 6)
